\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
% \usepackage{cfr-lm} % Comment or remove this line (CFR-LM font)
\usepackage[T1]{fontenc}
\usepackage{tgtermes} % TeX Gyre Termes (Times New Roman equivalent)
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}

\usepackage[most]{tcolorbox}
\tcbset{
	frame code={},
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{:\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.2mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}: \hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-1mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.1mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-1.4mm}
}

\newcommand{\resumeProject}[2]{
\vspace{0.3 mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        #1 & \footnotesize{#2} \\
    \end{tabular*}
    \vspace{-1mm}
}

\newcommand{\resumeProjectP}[3]{
\vspace{0.3 mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \text{\footnotesize{#2}} \\
        \large{#3}
    \end{tabular*}
    \vspace{-6.7 mm}
}

% \newcommand{\resumeSubItem}[2]{#1: #2\vspace{0.8pt}}
\newcommand{\resumeSubItem}[2]{
\vspace{0.3 mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        #1 & \footnotesize{#2} \\
    \end{tabular*}
    \vspace{-1mm}
}


\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.0mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{1mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-1mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-1mm}}
\newcommand{\cvsection}[1]{%
\vspace{1mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

\newcommand{\name}{Jatin Prajapati} % Your Name
\newcommand{\phone}{9425021595 } % Your Phone Number
\newcommand{\emaila}{\textcolor{blue}{jatinskytek@gmail.com}} %Email 
\newcommand{\emailb} {jatinskytek@gmail.com} %Email 2
\newcommand{\website} {Website} %Website
\newcommand{\github}{Github} %Github
\newcommand{\linkedin}{Linkedin} %linkedin
\begin{document}
% \fontfamily{cmr}\selectfont
%\scriptsize

\parbox{\linewidth}{%
    \centering
    \textbf{\LARGE \name} \\[0.5em]
    +91-\phone \hspace{0.4mm}$|$ 
    \emailb \hspace{0.4mm}$|$
    {\href{https://www.linkedin.com/in/jatin-skytek145/}{linkedin.com/in/jatin-skytek145}} $|$
    {\href{https://github.com/jatinskytek}{github.com/jatinskytek}} \hspace{0.4mm}\\
}



\vspace{-2mm}
%----Summary----%
\section{\textbf{Summary}}
{Machine Learning Engineer with 3 years of experience building scalable ML systems and production-grade computer vision pipelines. Strong background in model deployment, inference optimization, and data processing, with hands-on experience debugging real-world systems. Proven ability to design, evaluate, and improve ML models while collaborating across teams to deliver reliable and efficient solutions.}


\vspace{-2mm}
%-----------EXPERIENCE-----------------
\section{\textbf{Work Experience}}
 \resumeProject
  {\textbf{Machine Learning Engineer} | Droisys | Noida, Uttar Pradesh}
    {August 2025 – Present}
      \resumeItemListStart
      \item{Designed and deployed a YOLOv8-based object detection system for retail brand recognition in production environments.}

      \item{Improved inference latency by 25–40\% through optimization of preprocessing pipelines, batching strategies, and efficient resource utilization.}

      \item{Built scalable data pipelines for auto-annotation, dataset versioning, and few-shot labeling.}

      \item{Incorporated object shape-based training techniques to handle blurry and arbitrarily oriented samples, improving detection robustness in real-world scenarios.}

      \item{Implemented model evaluation and confidence-based filtering mechanisms to detect low-quality predictions, improving system reliability.}

      \item{Debugged production issues across model inference and data pipelines, ensuring system stability and performance.}
      \resumeItemListEnd


    \resumeProject
      {\textbf{Machine Learning Engineer} | CIPL | Noida, Uttar Pradesh}
      {July 2023 - July 2025}
        \resumeItemListStart
        \item{Developed and evaluated ML models for cryptographic analysis, simulating large-scale prediction attacks on 50+ cipher systems.}
        
        \item{Designed a neural cryptosystem (Alice–Bob–Eve) achieving >99\% accuracy, demonstrating secure communication via learned representations.}
        
        \item{Built evaluation pipelines using NIST test suites to validate randomness and model robustness.}
        
        \item{Applied adversarial ML techniques (FGSM, PGD) to analyze vulnerabilities and improve model robustness.}
        
        \item{Led development of a backdoor detection framework (TraceNet), focusing on scalable and interpretable ML security solutions.}
        \resumeItemListEnd
    \vspace{-3mm}    

\newcommand{\resumeProjectNoItemNoDate}[2]{
  \item #1 : {\small #2} \vspace{-2mm}
}


\section{\textbf{Projects}}
\vspace{2mm}
\begin{itemize}[leftmargin=0.15in]

\resumeProjectNoItemNoDate
{TraceNet – Backdoor Detection Framework}
{Developed a scalable gradient-based detection system for identifying backdoor attacks; improved detection speed by 10× on benchmark datasets.}

\resumeProjectNoItemNoDate
{Retail Product Recognition System}
{Built end-to-end CV pipelines using YOLOv8 and CLIP embeddings; evaluated trade-offs between accuracy, latency, and scalability for production use.}

\resumeProjectNoItemNoDate
{Adversarial Neural Cryptosystem}
{Designed and trained a neural network–based encoder–decoder system that transforms plaintext into encrypted data, generating highly randomized bit patterns and achieving 99.9\% secure communication accuracy with validated randomness properties.
.}

\resumeProjectNoItemNoDate
  {Hospital Readmission Prediction (HCUP 2016)}
  {Analyzed highly imbalanced (98:2) patient data to model readmission risk; delivered actionable insights in collaboration with University of Florida.}
\end{itemize}


% \vspace{-3 mm}
\section{\textbf{Research}}
\vspace{1 mm}

\resumeProjectP
  {Backdoor Detection in Deep Neural Networks (TraceNet)}{IEEE (ICDSINC, NIT Raipur) 2025}{}
  \resumeItemListStart
    \item Conducted research to detect and interpret backdoor attacks, achieving 10x faster detection speed than baseline methods while maintaining high accuracy and enhancing interpretability.
    \item Submitted work to IEEE conference focusing on scalable, interpretable AI security aligned with incident response best practices; experimental evaluation on 3 public datasets.
  \resumeItemListEnd

\resumeProjectP
  {Adversarial Neural Cryptography: Security Challenges and Solutions}{ICMC 2025 -- IIT Bhilai}{}
  \resumeItemListStart
    \item Presented findings analyzing vulnerabilities and robustness of neural cryptosystems under adversarial attacks, reducing model distinguishability to 50\%.
    \item Attained nearly 100\% plaintext retrieval accuracy by Bob from ciphertext, demonstrating strong cryptosystem reliability and effective mitigation of information leakage.
  \resumeItemListEnd
\vspace{-2 mm}
\section{\textbf{Skills}}
\vspace{2 mm}
\resumeItemListStart
\item{\textbf{Programming:} Python, SQL}

\item{\textbf{ML Systems:} Model Deployment, Model Evaluation, Data Pipelines, Debugging, Performance Optimization}

\item{\textbf{Machine Learning:} Supervised Learning, Clustering, PCA, XGBoost, SVM}

\item{\textbf{Deep Learning:} CNNs, GANs, LSTMs, Transfer Learning}

\item{\textbf{Computer Vision:} Object Detection (YOLO), Image Classification, Feature Extraction}

\item{\textbf{Frameworks:} PyTorch, TensorFlow, Scikit-learn, OpenCV}

\item{\textbf{Tools:} Git, Jupyter, Linux}
\resumeItemListEnd


%-----------EDUCATION-----------------
\vspace{-5 mm}
\section{\textbf{Education}}
\resumeProject  
  {Samrat Ashok Technological Institute, Madhya Pradesh}
  {March 2019 - March 2023}{B.Tech. - Computer Science Engineering}
\resumeItemListEnd
\end{document}
